---
title: "Quiz 4"
author: "Yuchan Jeong"
date: "`r Sys.Date()`"
output: html_document
---

#1 

A pharmaceutical company is interested in testing a potential blood pressure lowering medication. Their first examination considers only subjects that received the medication at baseline then two weeks later. Consider testing the hypothesis that there was a mean reduction in blood pressure? Give the P-value for the associated two sided T test. (Hint, consider that the observations are paired.) 

```{r}
a <- c(1, 2, 3, 4, 5)
b <- c(140, 138, 150, 148, 135)
c <- c(132, 135, 151, 146, 130)

df <- data.frame(a,b,c)
colnames(df) <- c("Subject", "Baseline", "Week 2");df
```

```{r}
t.test(df$Baseline, df$`Week 2`, alt = "two.sided", paired = TRUE)
```

#2
A sample of 9 men yielded a sample average brain volume of 1,100cc and a standard deviation of 30cc. What is the complete set of values of $\mu_0$ that a test of $H_0:\mu=\mu_0$ would fail to reject the null hypothesis in a two sided 5% Students t-test?

```{r}
sample_mean <- 1100
n = 9
sample_sd <- 30
alpha <- 0.05

z <- qt(p = alpha/2, df = (n-1), lower.tail = FALSE)

lower_bound <- sample_mean - z*(sample_sd/sqrt(9))
upper_bound <- sample_mean + z*(sample_sd/sqrt(9))
```


#3
Researchers conducted a blind taste test of Coke versus Pepsi. Each of four people was asked which of two blinded drinks given in random order that they preferred. The data was such that 3 of the 4 people chose Coke. Assuming that this sample is representative, report a P-value for a test of the hypothesis that Coke is preferred to Pepsi using a one sided exact test.

```{r}
binom.test(x = 3, n = 4, p = 0.5, alt = "greater")
```
#4
Infection rates at a hospital above 1 infection per 100 person days at risk are believed to be too high and are used as a benchmark. A hospital that had previously been above the benchmark recently had 10 infections over the last 1,787 person days at risk. About what is the one sided P-value for the relevant test of whether the hospital is below the standard? 
```{r}
poisson.test(x = 10, T = 1787, r = 0.01, alt = "less")
```

#5
Question 5
Suppose that 18 obese subjects were randomized, 9 each, to a new diet pill and a placebo. Subjects’ body mass indices (BMIs) were measured at a baseline and again after having received the treatment or placebo for four weeks. The average difference from follow-up to the baseline (followup - baseline) was −3 kg/m2 for the treated group and 1 kg/m2 for the placebo group. The corresponding standard deviations of the differences was 1.5 kg/m2 for the treatment group and 1.8 kg/m2 for the placebo group. Does the change in BMI appear to differ between the treated and placebo groups?  Assuming normality of the underlying data and a common population variance, give a pvalue for a two sided t test.

$t = \frac{\mu_1-\mu_2}{s_p \cdot \sqrt{\frac{1}{n_1}+\frac{1}{n_2}}}$

```{r}
n_1 <- 9
n_2 <- 9

mean_1 <- -3
mean_2 <- 1

sd_1 <- 1.5
sd_2 <- 1.8

s_p <- sqrt(((n_1-1)*(sd_1)^2+(n_2-1)*(sd_2)^2)/(n_1+n_2-2))
t = (mean_1-mean_2)/(s_p*sqrt((1/n_1)+(1/n_2)))

p_value <- 2 * pt(abs(t), df = (n_1+n_2-2), lower.tail = FALSE)
```

#7
Researchers would like to conduct a study of 100 healthy adults to detect a four year mean brain volume loss of $.01 mm^3$. Assume that the standard deviation of four year volume loss in this population is $.04mm^3$. About what would be the power of the study for a $5%$ one sided test versus a null hypothesis of no volume loss?

```{r}
power.t.test(n = 100, delta = 0.01, sd = 0.04, type = "one.sample", alt = "one.sided")
```

#8
Researchers would like to conduct a study of 100 healthy adults to detect a four year mean brain volume loss of $.01 mm^3$. Assume that the standard deviation of four year volume loss in this population is $.04mm^3$. About what would be the value of $n$ needed for $90%$ power of type one error rate of $5%$ one sided test versus a null hypothesis of no volume loss?



```{r}
power.t.test(power = 0.9, delta = 0.01, sd = 0.04, type = "one.sample", alt = "one.sided")
```


