---
title: "My Fancy Presentation"
author: "Yuchan Jeong"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My new slide
Plain text

*italicized text*

**Bold text**

`for (i %in% 1:10)`

***
A slide without a title

### A top level subheading

#### A second level subheading

## My Second Slide

This slide shows that comment = "" remove ## in front of the data sets outcome

```{r, comment = "", echo = TRUE}
head(mtcars)
```

## My Third Slide

This slide shows that eval = FALSE give no outcome
```{r, comment = "", echo = TRUE, eval = FALSE}
head(mtcars)
```

## My Fourth Slide

This slide shows that fig.align moves plot to the centre of the slide and fig.cap shows the title of the plot
```{r, echo = FALSE, fig.align='center', fig.cap='My Awesome figure'}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

