---
title: "Quiz_1"
author: "Yuchan Jeong"
date: "`r Sys.Date()`"
output: html_document
---
---
title: "Quiz_1"
author: "Yuchan Jeong"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

#1 
Consider the data set given below
```{r}
x <- c(0.18, -1.54, 0.42, 0.95)
```

And weights given by
```{r}
w <- c(2, 1, 3, 1)
```

Give the value of $\mu$  that minimizes the least squares equation
$\sum^n_{i=1}w_i(x_i-\mu)^2$

Remember that 
$\mu = \frac{\sum^n_{i=1}X_iw_i}{\sum^n_{i=1}w_i}$


```{r}
mu <- sum(x*w) / sum(w); mu
```
#2
Consider the following data set
```{r}
x <- c(0.8, 0.47, 0.51, 0.73, 0.36, 0.58, 0.57, 0.85, 0.44, 0.42)
y <- c(1.39, 0.72, 1.55, 0.48, 1.19, -1.59, 1.23, -0.65, 1.49, 0.05)
```

Fit the regression through the origin and get the slope treating y as the outcome and x as the regressor. (Hint, do not center the data since we want regression through the origin, not through the means of the data.)


```{r}
fit <- lm(y~x-1)
summary(fit)
```
#3
Do data(mtcars) from the datasets package and fit the regression model with mpg as the outcome and weight as the predictor. Give the slope coefficient.

```{r}
data(mtcars)

fit2 <- lm(mtcars$mpg ~ mtcars$wt)
summary(fit2)
```
#6

Consider the data given by the following
```{r}
x <- c(8.58, 10.46, 9.01, 9.64, 8.86)
```
What is the value of the first measurement if x were normalized (to have mean 0 and variance 1)?
```{r}
mean_x <- mean(x)
normalized_x1 <- (x[1]-mean_x)/sd(x); normalized_x1
```
#7
Consider the following data set (used above as well). What is the intercept for fitting the model with x as the predictor and y as the outcome?
```{r}
x <- c(0.8, 0.47, 0.51, 0.73, 0.36, 0.58, 0.57, 0.85, 0.44, 0.42)
y <- c(1.39, 0.72, 1.55, 0.48, 1.19, -1.59, 1.23, -0.65, 1.49, 0.05)

fit3 <- lm(y~x)
summary(fit3)
```
#9
Consider the data given by

```{r}
x <- c(0.8, 0.47, 0.51, 0.73, 0.36, 0.58, 0.57, 0.85, 0.44, 0.42)
mean(x)
```
What value minimizes the sum of the squared distances between these points and itself?