---
title: "Quiz_3"
author: "Yuchan Jeong"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(AppliedPredictiveModeling)
library(ggplot2)
library(lattice)
library(caret)
library(ElemStatLearn)
```


#1
1. Subset the data to a training set and testing set based on the Case variable in the data set. 
2. Set the seed to 125 and fit a CART model to predict Class with the rpart method using all predictor variables and default caret settings. 
3. In the final model what would be the final model prediction for cases with the following variable values:
a. TotalIntench2 = 23,000; FiberWidthCh1 = 10; PerimStatusCh1=2 
b. TotalIntench2 = 50,000; FiberWidthCh1 = 10;VarIntenCh4 = 100 
c. TotalIntench2 = 57,000; FiberWidthCh1 = 8;VarIntenCh4 = 100 
d. FiberWidthCh1 = 8;VarIntenCh4 = 100; PerimStatusCh1=2 
TIP: Plot the resulting tree and to use the plot to answer this question.


```{r}
data(segmentationOriginal)
training <- subset(segmentationOriginal, Case == "Train")
test <- subset(segmentationOriginal, Case == "Test")
predictors <- setdiff(names(training), c("Case", "Class", "Cell"))
set.seed(125)
```


# a. TotalIntench2 = 23,000; FiberWidthCh1 = 10; PerimStatusCh1 = 2 
```{r}
predictors_a <- c("TotalIntenCh2", "FiberWidthCh1", "PerimStatusCh1")
modFit_a <- train(x = training[, predictors_a], y = training$Class, method = "rpart")

new_data_a <- data.frame(
  TotalIntenCh2 = 23000,
  FiberWidthCh1 = 10,
  PerimStatusCh1 = 2
)

predict(modFit_a, newdata = new_data_a)
```

# b. TotalIntench2 = 50,000; FiberWidthCh1 = 10;VarIntenCh4 = 100 

```{r}
predictors_b <- c("TotalIntenCh2", "FiberWidthCh1", "VarIntenCh4")

modFit_b <- train(x = training[, predictors_b], y = training$Class, method = "rpart")

new_data_b <- data.frame(
  TotalIntenCh2 = 50000,
  FiberWidthCh1 = 10,
  VarIntenCh4 = 100
)

predict(modFit_b, newdata = new_data_b)

```

# c. TotalIntench2 = 57,000; FiberWidthCh1 = 8;VarIntenCh4 = 100 

```{r}
predictors_c <- c("TotalIntenCh2", "FiberWidthCh1", "VarIntenCh4")

modFit_c <- train(x = training[, predictors_c], y = training$Class, method = "rpart")

new_data_c <- data.frame(
  TotalIntenCh2 = 57000,
  FiberWidthCh1 = 8,
  VarIntenCh4 = 100
)

predict(modFit_c, newdata = new_data_c)
```


# d. FiberWidthCh1 = 8;VarIntenCh4 = 100; PerimStatusCh1=2 


```{r}
predictors_d <- c("FiberWidthCh1", "VarIntenCh4", "PerimStatusCh1")

modFit_d <- train(x = training[, predictors_d], y = training$Class, method = "rpart")

new_data_d <- data.frame(
  FiberWidthCh1 = 8,
  VarIntenCh4 = 100,
  PerimStatusCh1 = 2
)

predict(modFit_d, newdata = new_data_d)
```


#3

```{r}
load("C:\\Users\\PC\\Documents\\GitHub\\datasciencecoursera\\8. Practical Machine Learning\\Quiz\\olive.rda")
olive = olive[,-1]
```

```{r}
treeFit <- rpart(Area ~., data = olive)
modFit <- train(Area ~., data = olive, method = "rpart")

newdata = as.data.frame(t(colMeans(olive)))

predict(treeFit, newdata)
predict(modFit, newdata)
```
```
2.783. It is strange because Area should be a qualitative variable - but tree is reporting the average value of Area as a numeric variable in the leaf predicted for newdata
```
```{r}
olive$Area <- as.factor(olive$Area)

treeFit <- rpart(Area ~., data = olive)
modFit <- train(Area ~., data = olive, method = "rpart")

predict(treeFit, newdata)
predict(modFit, newdata)
```


#4
Load the South Africa Heart Disease Data and create training and test sets with the following code:

```{r}
library(ElemStatLearn)
data(SAheart)
set.seed(8484)
train = sample(1:dim(SAheart)[1], size = dim(SAheart)[1]/2, replace = FALSE)
trainSA = SAheart[train, ]
testSA  = SAheart[-train, ]
```
Then set the seed to 13234 and fit a logistic regression model  (method="glm", be sure to specify family="binomial") with Coronary Heart Disease (chd) as the outcome and age at onset, current alcohol consumption, obesity levels, cumulative tabacco, type-A behavior, and low density lipoprotein cholesterol as predictors. Calculate the misclassification rate for your model using this function and a prediction on the "response" scale:
```{r}
set.seed(13234)
model <- train(
  chd ~ age + alcohol + obesity + tobacco + typea + ldl,
  data = trainSA,
  method = "glm",
  family = "binomial"
)

pred <- predict(model, newdata = testSA, type = "prob") # ❌ 여기선 확률이 안 나옴 (glm은 factor일 때만)
```

```{r}
glm_fit <- model$finalModel

pred <- predict(glm_fit, newdata = testSA, type = "response")

missClass <- function(values, prediction){
  sum(((prediction > 0.5) * 1) != values) / length(values)
}

train_error <- missClass(trainSA$chd, predict(glm_fit, newdata = trainSA, type = "response"))
test_error  <- missClass(testSA$chd, pred)

train_error
test_error
```
