---
title: "Project"
author: "Yuchan Jeong"
date: "`r Sys.Date()`"
output: html_document
---
```{r include=FALSE}
library(caret)
library(doParallel)
```

# 1. Introduction
The objective of this project is to use machine learning to predict the manner in which an exercise was performed—correctly or in one of four incorrect ways. This is a classification problem where the target variable is classe, and the predictors are derived from accelerometer data collected from various locations (belt, forearm, arm, and dumbbell) on six participants.

The classe variable has five possible outcomes:
```
A: Correctly performed

B, C, D, E: Incorrectly performed in four distinct ways
```
The model needs to be robust, highly accurate, and provide a reliable estimate of its expected performance on unseen data (out-of-sample error).

# 2. Data Loading and Preprocessing
We begin by loading the training and testing datasets. A critical step in preprocessing this dataset is handling the numerous columns that contain mostly missing values (NA) or have near-zero variance. These columns provide no predictive power and can hinder model performance and efficiency. 
```{r}
setwd("C:\\Users\\PC\\Documents\\GitHub\\datasciencecoursera\\8. Practical Machine Learning\\Project")

if (isFALSE(("pml-training.csv" %in% list.files(getwd())))) {
        url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
        download.file(url, file.path(getwd(), "pml-training.csv"))
        pml_training <- read.csv("pml-training.csv", row.names = 1, na.strings = c("NA", "#DIV/0!", ""))
} else pml_training <- read.csv("pml-training.csv", row.names = 1, na.strings = c("NA", "#DIV/0!", ""))


if (isFALSE(("pml-testing.csv" %in% list.files(getwd())))) {
        url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
        download.file(url, file.path(getwd(), "pml-testing.csv"))
        pml_testing <- read.csv("pml-testing.csv", row.names = 1, na.strings = c("NA", "#DIV/0!", ""))
} else pml_testing <- read.csv("pml-testing.csv", row.names = 1, na.strings = c("NA", "#DIV/0!", ""))
```
## 2.1 Filtering Near-Zero Variance and Missing Data

We filter the data based on two criteria:

**Redundant/Identifier Columns:** Remove the first 6 columns which are identifiers (e.g., user_name, raw_timestamp_hex) and do not contribute to predicting the physical activity.

*Missing Values (NA):** Remove columns that contain a high percentage of missing values. Given the nature of the data, we will remove any column with more than 60% missing data, as determined by an initial exploratory pass (many columns are almost entirely NA).

```{r}
pml_training <- pml_training[, -c(1:6)]
pml_testing <- pml_testing[, -c(1:6)]
```

```{r}
set.seed(42)
na_ratio <- colSums(is.na(pml_training)) / nrow(pml_training)
valid_cols <- names(na_ratio[na_ratio < 0.6]) # Keep columns with < 60% NA

training_final <- pml_training[ ,valid_cols]

training_final$classe <- as.factor(training_final$classe)

intrain <- createDataPartition(y = training_final$classe, p = 0.7, list = FALSE)

training_data <- training_final[intrain,]
validate_data <- training_final[-intrain,]
```

# 3. Model Building: Random Forest

## 3.1 Choice of Algorithm

We chose the Random Forest algorithm for several key reasons:

```
High Accuracy: Random Forest (RF) is a non-linear ensemble method that typically yields high accuracy in complex classification tasks.

Robustness to Overfitting: By building an ensemble of decision trees, RF is highly resistant to overfitting, even without aggressive hyperparameter tuning.

Automatic Feature Selection: RF inherently handles irrelevant predictors and estimates variable importance, which is useful for interpretation.

Efficiency: It runs quickly and efficiently on large datasets.
```

# 3.2 Training the Model
Although Random Forest is an excellent algorithm, its primary drawback is its slow speed due to the numerous trees it builds. To address this, I chose to implement parallel processing instead of standard serial processing to distribute the computational load and significantly maximize efficiency during the training phase.
```{r}
cores <- detectCores()
cl <- makeCluster(cores - 1) 
registerDoParallel(cl)
```

```{r}
set.seed(42)
time_check <- system.time({
      model_rf <- train(classe ~., 
                  method = "rf", 
                  data = training_data, 
                  trControl = trainControl(method = "cv", number = 3)
)
})

stopCluster(cl)
time_check
```

# 3.3 Check model performance
We must assess the model's performance. First, we use the predict function to determine the model's predicted outcomes on the validate_data. Subsequently, we use the confusionMatrix to calculate the final accuracy and evaluate the model's overall efficacy.
```{r}
pred_valid <- predict(model_rf, validate_data)
```

```{r}
actual_labels <- validate_data$classe

pred_valid <- factor(pred_valid)
actual_labels <- factor(actual_labels)

levels(pred_valid) <- levels(actual_labels)
```

```{r}
cm_result <- confusionMatrix(data = pred_valid, reference = actual_labels)
print(cm_result)
```

```
Given that the model achieved an accuracy exceeding 99% on the validation data, we conclude that the model is well-trained and exhibits strong generalization capability.
```

# 3.4 Prediction testing data
```{r}
pred_final <- predict(model_rf, pml_testing[,-ncol(pml_testing)])
print(pred_final)
```

